Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-10-28 paper/main.tex
rewrite intro2

% brain mapping via fMRI
Humans can perceive and make sense of their daily environment casually and
seemingly without any effort. Cognitive neuroscientists use brain imaging
techniques to map seemingly effortless perceptual and cognitive processes like
seeing and recognizing faces (e.g. \citep{kanwisher1997ffa}) to functional brain
areas or networks.
% What is the PPA?
A classic example of a higher-level visual area is the ``parahippocampal place
area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}, and thus not anatomically but functionally
defined:
% neural correlate of scene perception
increased hemodynamic activity is observed in the PPA when subjects view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
tools or faces) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
epstein1998ppa}.

>>>>

% brain mapping via fMRI
Humans can perceive and make sense of their daily environment casually and
seemingly without any effort. Cognitive neuroscientists use brain imaging
techniques to map perceptual and cognitive processes (e.g. seeing and
recognizing faces; \citep{kanwisher1997ffa}) to functional brain areas or
networks.
% What is the PPA?
A classic example of a higher-level visual area is the ``parahippocampal place
area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}, and thus not anatomically but functionally
defined:
% neural correlate of scene perception
increased hemodynamic activity is observed in the PPA when subjects view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
tools or faces) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
epstein1998ppa}.
